---
title: "Teaching and Education"
output: 
  html_document:
   theme: flatly
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

<br>
Hello and Welcome! <br>
My name is Tahir Muhammad and I am a Teaching Assistant at University of Toronto. The following website contains the contents which I use to teach my students, and some additional resources to set them up for success. Please feel free to look around, and if you have any inquiries, questions or recommendations -- please don't hesitate to let me know. 

### My Teaching Philosophy in a Nutshell

I strongly believe in the ability of the the human brain to learn and grasp anything with consistent effort. In order to bring the best out of my students in the fields of statistics, computer science, mathematics and data science, I try to convey my enthusiasm in my lessons and show how these domains are impacting the world around us everyday. By teaching content that is engaging and focusing on the how and why we do things in this manner rather than just memorizing how to solve an equation or code a problem empowers the students to be critical thinkers. Striking a balance between the big picture, the underlying mathematical concepts and the practical implementation is crucial for a learners journey in these domains, and I try to do just that for my students. 

### Teaching Experience (University of Toronto)

#### Statistics

- STA107 - Probability and Reasoning
- STA130 - Statistical Reasoning and Data Science 
- STA237 - Data Analysis I 
- STA238 - Data Analysis II
- STA302/STA2002 - Regression Analysis

### Cool things
__Look at how cool this plot is!__

$$Y = \alpha \cdot \sin(X), \alpha = 0,0.1,0.2,...,3$$

```{r, echo = FALSE, fig.align='center'}
library(tidyverse)
cool_function <- function(x, alpha) return(sin(alpha*x))
xs <- seq(0, pi*1.5, 0.005)
ys <- cool_function(xs, 1)
results <- data_frame(xs, ys, alpha = "1")
for(alpha in seq(0,3, 0.1)){
  results <- results %>% 
    bind_rows(data_frame(
      xs, 
      ys = cool_function(xs, alpha),
      alpha = as.character(alpha)
    ))
}

ggplot(results, aes(x = xs, y = ys, color = alpha)) + 
  geom_line() + 
  theme_bw() + 
  theme(legend.position="none")
```

# Render and run the site
rmarkdown::render_site()
```{r, echo = FALSE}
# Render and run the site
#rmarkdown::render_site()
# list which files will be removed
#rmarkdown::clean_site(preview = TRUE)

# actually remove the files
#rmarkdown::clean_site()
```
