---
title: "An Introduction to Probability and Modelling"
date: "Winter 2021" 
output: 
  html_document:
   toc: true
   toc_depth: 5
   toc_float: true 
   theme: flatly
---

Hello and Welcome! <br>
My name is Tahir Muhammad, and I am your TA for STA107 this semester. I will be mainly using this site to present your relevant weekly tutorials, and end off with additional resources / practice problems in order to help you succeed in this course. If you have any suggestions, recommendations, or any form of feedback which you would like me to know, please use the Feedback Form in top right corner to let me know (Anonymous options aswell!)

- <span class="glyphicon glyphicon-user" aria-hidden="true"></span> Tahir Muhammad, Tahir.muhammad@mail.utoronto.ca 

- Tutorial Times are Friday 2-3 PM, and Office hours are on Wednesday 6-7 PM <br>
You can find all of the Teaching Assistant tutorials, and office hours information at
[www.Quercus/STA107/TAs.com](https://q.utoronto.ca/courses/212245/pages/zoom-links-to-tutorials-and-ta-office-hours?module_item_id=2195690)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Week 1

## Agenda for today:

- Introductions 
- Vocabulary Review
- R basics 

## Introductions

Ice Breakers -- Your name, Program of study, one thing that you absolutely love / or one thing that you absolutely hate about quarantine

## Vocabulary Review

## R basics

The plan today is to cover lots of R basics, so you can see what R is capable of and learn these concepts on your own. 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
## Including Plots 2

ahahdas

## Including Plots 3

ashda
